Simulating the Linux page cache in distributed applications with the WRENCH library

### 2020-12-08 paper_io_sim.tex
edits in results

@@

@@

			The I/O time of tasks in simulators and real execution is also tracked and compared.
			Fig.~\ref{fig:single_error} shows the relative error of simulated I/O time
			of individual I/O activities.
			Our pipeline consists of 3 tasks, and each task reads an input file,
			performs some computation, and writes output file.
			Thus, there are 6 sequential I/O activities, \textit{Read 1} and \textit{Write 1}
			from the first task, \textit{Read 2} and \textit{Write 2} the second task,
			and \textit{Read 3}, \textit{Write3} from the last task.

			\begin{figure*}
			\centering
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
			\end{subfigure}
			\caption{Memory profiling results with different input file sizes.
			The bars in the figures present activities in tasks (read, compute and write),
			the lines describe memory status throughout run time of the pipeline.}
			\label{fig:single_memprof}
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O operation. 
   			\textcolor{red}{Update real results of 20GB}}
			\end{figure*}

			In general, with all input sizes in the experiment, the simulation errors
			of simulators with page cache model (Python and WRENCH-cache simulators)
			are remarkably lower than the result with original WRENCH .
			The reason is, in original WRENCH, because page cache is not simulated,
			data is only read and written with disk bandwidth, which is much slower
			than memory bandwidths, leading to simulated I/O time longer than in reality.
			Especially, the simulation time errors of \textit{Read 3} with 100 GB of input
			in the simulators with page cache are just under the error in original WRENCH.
			This longer read can be explained with the amount of cached data of files
			at the beginning of the read in reality and simulators shown in
			Fig.~\ref{fig:single_cache}.
			In this figure, \textit{file $<$i$>$} is the input of \textit{Read $<$i$>$} and
			output of \textit{Write $<$i-1$>$}.
			With the input size of 20 GB, in both real execution and WRENCH-cache
			simulator, there is no difference in the page cache since all files in the
			pipeline can be entirely cached.
			With the input of 100 GB, the difference between real execution and WRENCH-cache
			simulator can be seen in the amount of \textit{file 3} cache after \textit{Write 2}.
			In real execution, after being written by \textit{Write 2},
			\textit{file 3} is entirely in cache.
			Thus, in \textit{Read 3}, \textit{file 3} is read with memory bandwidth.
			However, in the WRENCH-cache simulator, only a part of \textit{file 3} is
			cached after \textit{Write 2}, which means \textit{Write 2} reads a part of
			\textit{file 3} from disk.
			The reason for the difference is in our WRENCH-cache simulator,
			with 100 GB of input, while \textit{file 3} is being written,
			the page cache is saturated, eviction is then evoked to evict data
			from page cache and make space available for \textit{file 3}.
			However, because the evicted amount is less than required,
			some \textit{file 3} data is evicted after being written, make \textit{file 3}
			partially cached.
			As a result, in \textit{Read 3}, only a part of \textit{file 3} is read from cache
			with memory bandwidth, a part of it is read from disk with disk read bandwidth,
			which is many times slower, leading to longer read time.

>>>>

            \tristan{mention that cache was flushed before each experiment}

@@

        Figure~\ref{fig:single_error} shows the relative error of simulated
        read and write times throughout the three application tasks. The
        page cache simulation model drastically reduces simulation errors
        for all I/O operations except the first read that deals with
        uncached data. Errors are reduced from an average of \texttt{xxx\%}
        in WRENCH to \texttt{yyy \%} in the Python prototype and
        \texttt{zzz \%} in WRENCH-cache. The original WRENCH simulator significantly overestimates
        read and write times, due to its lack of page cache simulation
        model.

        % In this figure, \textit{file $<$i$>$} is the input of \textit{Read $<$i$>$} and
        % output of \textit{Write $<$i-1$>$}.
        With the input size of 20 GB, in both real execution and WRENCH-cache
        simulator, there is no difference in the page cache since all files in the
        pipeline can be entirely cached \tristan{what does this refer to? 
        For 20 GB there is still some error in WRENCH-cache, what do you mean ``there is no difference in the page cache''?}.

        With the input of 100 GB, the difference between real execution and WRENCH-cache
        simulator can be seen in the amount of \textit{file 3} cache after \textit{Write 2}.
        In real execution, after being written by \textit{Write 2},
        \textit{file 3} is entirely in cache.
        Thus, in \textit{Read 3}, \textit{file 3} is read with memory bandwidth.
        However, in the WRENCH-cache simulator, only a part of \textit{file 3} is
        cached after \textit{Write 2}, which means \textit{Write 2} reads a part of
        \textit{file 3} from disk.
        The reason for the difference is in our WRENCH-cache simulator,
        with 100 GB of input, while \textit{file 3} is being written,
        the page cache is saturated, eviction is then evoked to evict data
        from page cache and make space available for \textit{file 3}.
        However, because the evicted amount is less than required,
        some \textit{file 3} data is evicted after being written, make \textit{file 3}
        partially cached.
        As a result, in \textit{Read 3}, only a part of \textit{file 3} is read from cache
        with memory bandwidth, a part of it is read from disk with disk read bandwidth,
        which is many times slower, leading to longer read time.

@@

            \begin{figure*}
            \centering
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
            \end{subfigure}
            \caption{Simulation errors with different input file sizes}
            \label{fig:single_error}
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
            \end{subfigure}
            \caption{Memory profiling results with different input file sizes.
            The bars in the figures present activities in tasks (read, compute and write),
            the lines describe memory status throughout run time of the pipeline.}
            \label{fig:single_memprof}
            \begin{subfigure}{\linewidth}
                \centering
                   \includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
            \end{subfigure}
            \label{fig:single_cache}
               \caption{Amount of file data in cache after each I/O operation. 
               \textcolor{red}{Update real results of 20GB}}
            \end{figure*}
